Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with Uniform Kernels

### 2016-02-28 main_paper.tex
Add a few small citations to the introduction

This bootstrap procedure can offer some advantages over analytical methods in
this setting. In particular, both this paper and CCT assume that the
observations are generated independently of each other; extending these bias
correction methods to other forms of dependence is relatively straightforward
for the bootstrap but can be substantially more complicated for analytical
corrections, which have to be explicitly derived by the researcher. Similarly,
although we only provide results for the local linear model in this paper, it is
trivial to implement this procedure for higher order polynomials, for
covariate-adjusted estimators \citep{calonico2015}, or for other local
smoothers. \citep{loader2006} However, in this paper we focus on the baseline
case of sharp RD with a local linear model and uniform kernel. Extensions to
fuzzy RD designs\footnote{%
  ``Fuzzy'' regression discontinuity design \citep{HTV2001}, as opposed to
  ``sharp'' RD, describes situations where the probability of treatment changes
  discontinuously at a known threshold, but by less than 100\%. Then there are
  treated and untreated subjects above and below the discontinuity but the
  treatment effect remains identified.} %
and nonuniform kernels, which require nontrivial changes to the underlying
bootstrap algorithm, as well as developments to address cross sectional
dependence, are the subject of ongoing research.

@@

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design. We focus on the linear case for ease in
  exposition.} %
For this model, if $h$ represents a bandwidth parameter, the estimator
of $\tau$, $\hat\tau(h)$, is
\begin{equation}
  \label{eq:13}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{0 > X_{i} > -h_n \} (Y_{i} - \beta_{0} - X_{i} \beta_{1})^{2}.
\end{align*}

>>>>

This bootstrap procedure can offer some advantages over analytical methods in
this setting. In particular, both this paper and CCT assume that the
observations are generated independently of each other; extending these bias
correction methods to other forms of dependence is relatively straightforward
for the bootstrap but can be substantially more complicated for analytical
corrections, which have to be explicitly derived by the researcher. Similarly,
although we only provide results for the local linear model in this paper, it is
trivial to implement this procedure for higher order polynomials, for
covariate-adjusted estimators (\citealp{frolich2007}, \citealp{calonico2015}),
or for other local smoothers. \citep{loader2006} However, in this paper we focus
on the baseline case of sharp RD with a local linear model and uniform
kernel. Extensions to fuzzy RD designs\footnote{%
  ``Fuzzy'' regression discontinuity design \citep{HTV2001}, as opposed to
  ``sharp'' RD, describes situations where the probability of treatment changes
  discontinuously at a known threshold, but by less than 100\%. Then there are
  treated and untreated subjects above and below the discontinuity but the
  treatment effect remains identified.} %
and nonuniform kernels, which require nontrivial changes to the underlying
bootstrap algorithm, as well as developments to address cross sectional
dependence, are the subject of ongoing research.

@@

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}. We focus on the linear
  case for ease in exposition.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is
\begin{equation}
  \label{eq:13}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{0 > X_{i} > -h_n \} (Y_{i} - \beta_{0} - X_{i} \beta_{1})^{2}.
\end{align*}
